Compilation and Backend-Independent Vectorization for Multi-Party Computation

### 2022-05-02 overleaf/results.tex
Results minor change.

Therefore, MOTION's compiler performs analysis that informs circuit generation. In the above example, 
MOTION does the standard divide-and-conquer accumulation. The example also illustrates the limitation of higher-level AST analysis --- while 
the analysis was able to detect the associative accumulation when operator {\sf += } was used, it was unable to do so when an equivalent 
code was used. We conjecture that MPC source, as a more straight-forward representation will
not only enable detection of general associative loops, but also allow for program synthesis to increase opportunities for divide-and-conquer
parallelization~\cite{Farzan:2021}; we leave this as future work.

>>>>

Therefore, MOTION's compiler performs analysis that informs circuit generation and the example illustrates the power of the analysis. In the above example, 
MOTION does the standard divide-and-conquer accumulation. It also illustrates the limitation of higher-level AST analysis --- while 
the analysis was able to detect the associative accumulation when operator {\sf += } was used, it was unable to do so when an equivalent 
code was used. We conjecture that MPC source, as a more straight-forward representation will
not only enable detection of general associative loops, but also allow for program synthesis to increase opportunities for divide-and-conquer
parallelization~\cite{Farzan:2021}; we leave this as future work.
